\label{ch:conclusion_future}

\section{Conclusion}
This project successfully designed and implemented \textbf{Barqi Bazar}, a service oriented digital marketplace that integrates Point of Sale (POS) operations, administrative portals, and a rider based delivery system into a unified platform. The system enables Store Admins to manage products and perform sales through POS, submit product proposals for online publishing, and maintain local inventory, while Franchise Admins review and approve proposals to ensure centralized control and consistency across regions.

The platform also supports customer order placement, real time order tracking, rider bidding, and automated order routing, which collectively improve operational efficiency and delivery transparency. The inclusion of Super Admin controls for managing franchises, cities, and riders ensures scalability and governance across multiple operational regions.

Through modular design, well defined workflows, and clear separation of responsibilities among system roles, Barqi Bazar demonstrates an effective approach to bridging offline retail operations with online marketplaces and on demand delivery services. The project fulfills its core objectives and provides a solid foundation for a scalable, maintainable, and extensible digital commerce ecosystem.

\section{Limitations}
Despite meeting the primary goals, the system has certain limitations:
\begin{itemize}
	\item \textbf{Dependence on network connectivity:} Real time operations such as order tracking and rider bidding rely on stable internet access.
	\item \textbf{Limited automation in decision making:} Proposal reviews and rider selection are rule based and require manual administrative actions.
	\item \textbf{Basic analytics support:} The current implementation focuses on operational workflows rather than advanced business intelligence.
	\item \textbf{Manual scaling effort:} While service oriented, deployment and scaling require administrative configuration.
\end{itemize}

\section{Future Work}
Several enhancements can further strengthen Barqi Bazar in future iterations:

\subsection{Advanced Analytics and Reporting}
Future versions may include detailed dashboards for sales trends, inventory forecasting, rider performance metrics, and city wise demand analysis to support data driven decision making.

\subsection{Smart Rider Assignment}
Machine learning techniques can be introduced to automatically evaluate rider bids based on distance, rating, delivery history, and availability, enabling optimized delivery assignment.

\subsection{Enhanced Mobile Applications}
Dedicated mobile applications for customers, riders, and store admins can improve usability, accessibility, and real time interaction across the platform.

\subsection{Payment and Wallet Integration}
Secure digital payment gateways and wallet based transactions can be added to streamline order payments, rider earnings, and franchise settlements.

\subsection{Scalability and Cloud Deployment}
Deploying the system on cloud infrastructure with containerization can improve fault tolerance, scalability, and performance across multiple cities and franchises.

\subsection{Security and Compliance Enhancements}
Future work may include advanced authentication mechanisms, audit logs, and compliance features to meet regulatory and data protection requirements.

Overall, Barqi Bazar has strong potential to evolve into a full scale, intelligent marketplace platform that supports modern retail, logistics, and delivery operations across diverse regions.
