\label{ch:testing}

\section{Introduction}
Software testing ensures that the Barqi Bazar platform functions accurately, securely, and reliably.
Since the system includes multiple administrative modules (Point of Sale, Franchise Management,
Contract Management, and Order Management) along with role based access control, thorough testing
is required to verify correct behavior across all workflows.

This chapter describes the testing objectives, testing environment, and testing methods applied
to validate key operations such as authentication, POS sales, franchise/city management,
contract proposal handling, and order processing. It also presents executed test cases and results,
confirming that the system is stable and ready for deployment.

\section{Testing Objectives}
The goal of testing in Barqi Bazar is to ensure that all modules function correctly, reliably,
and securely under normal and edge case conditions. Testing was performed to verify system
workflows from admin side configuration to operational execution.

Key objectives include:
\begin{itemize}
	\item \textbf{Functional Verification:} Confirm each module works as intended (POS, Franchise, Contract, Orders).
	\item \textbf{Integration Validation:} Ensure smooth interaction between frontend dashboards, backend APIs, and database.
	\item \textbf{Data Accuracy:} Maintain consistency across all CRUD operations and transactional updates.
	\item \textbf{Performance Testing:} Validate responsiveness for listing screens and high activity actions (order updates, product search).
	\item \textbf{Security Enforcement:} Verify permission based access and restricted operations for different roles.
	\item \textbf{UI/UX Validation:} Ensure screens are usable, clear, and role appropriate for administrators and managers.
	\item \textbf{Error Handling:} Confirm validation and failure messages appear correctly for invalid inputs.
	\item \textbf{Deployment Readiness:} Confirm platform stability for real operational use.
\end{itemize}

\section{Testing Environment}
\subsection{Hardware Environment}
\begin{itemize}
	\item Laptop/PC with at least 8GB RAM and Intel i5 (or equivalent).
	\item Stable internet connection for API requests and database connectivity.
\end{itemize}

\subsection{Software Environment}
\begin{itemize}
	\item \textbf{Frontend:} React.js (Admin/Store dashboards), Tailwind CSS.
	\item \textbf{Backend:} REST APIs (project backend services).
	\item \textbf{Database:} PostgreSQL (core data storage).
	\item \textbf{Testing Tools:} Postman (API testing), Browser DevTools (UI/network debugging), pgAdmin/DBeaver (database verification).
\end{itemize}

\subsection{Test Data Environment}
\begin{itemize}
	\item Sample accounts for Super Admin, Franchise Admin, and Store Manager roles.
	\item Sample products, inventory records, and categories for POS testing.
	\item Sample franchises and cities for management workflows.
	\item Sample contract proposals and contract records for approval testing.
	\item Sample orders with different statuses for order lifecycle validation.
\end{itemize}

\section{Types of Testing}
\subsection{Unit Testing}
Unit testing was applied to validate individual components in isolation such as:
API endpoints, form validations, and core business rule functions (e.g., stock deduction, status transitions).

\subsection{Integration Testing}
Integration testing validated communication between:
\begin{itemize}
	\item Frontend dashboard actions and backend APIs
	\item Backend services and PostgreSQL persistence
	\item Multi module dependencies (e.g., POS sale updates inventory; order status updates affect tracking views)
\end{itemize}

\subsection{Functional Testing}
Functional testing verified complete feature workflows such as:
\begin{itemize}
	\item Authentication and role based dashboard access
	\item POS product listing, adding products, and sales execution
	\item Franchise creation and city assignment
	\item Contract creation, proposal listing, and approval/rejection
	\item Order listing, order status updates, and operational tracking
\end{itemize}

\subsection{System Testing}
System testing validated end to end behavior across modules to ensure:
workflow completeness, correct permissions, UI consistency, and stable database state.

\subsection{Performance Testing}
Performance testing focused on:
\begin{itemize}
	\item Page load time for listing dashboards (products, orders, contracts)
	\item API response time for search/filter operations
	\item Stability under repeated operations (bulk order updates, repeated product actions)
\end{itemize}

\subsection{Security Testing}
Security testing validated:
\begin{itemize}
	\item Authentication/session handling
	\item Role based access restrictions (admin only actions blocked for store managers)
	\item Input validation to prevent invalid or harmful requests
\end{itemize}

\subsection{User Acceptance Testing (UAT)}
UAT ensured real users could operate the system reliably:
navigation clarity, correct module behavior, and predictable outcomes for day to day store operations.

\section{Test Cases}
This section presents key test cases executed to validate Barqi Bazar core workflows including authentication,
POS operations, franchise governance, contract processing, and order lifecycle management.
Each test case outlines the objective, steps, expected result, and outcome.

% -------------------------
% Helper style: simple two-column table
% -------------------------

\subsection{Login Test Case (Valid Credentials)}
\begin{table}[H]
	\centering
	\caption{Test Case TC-01: Login (Valid Credentials)}
	\label{tab:tc_login_valid}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-01 \\ \hline
		\textbf{Brief Description} & Login using valid credentials and redirect user to the correct role based dashboard. \\ \hline
		\textbf{Precondition} & User account exists and is active in the system. \\ \hline
		\textbf{Steps} & Enter valid email/username and password $\rightarrow$ Click Login. \\ \hline
		\textbf{Expected Result} & Login successful and user redirected to role based dashboard (Super Admin / Franchise Admin / Store Manager). \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{Login Test Case (Invalid Credentials)}
\begin{table}[H]
	\centering
	\caption{Test Case TC-02: Login (Invalid Credentials)}
	\label{tab:tc_login_invalid}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-02 \\ \hline
		\textbf{Brief Description} & Validate login failure when incorrect credentials are entered. \\ \hline
		\textbf{Precondition} & Login screen is accessible. \\ \hline
		\textbf{Steps} & Enter incorrect email/password $\rightarrow$ Click Login. \\ \hline
		\textbf{Expected Result} & Error message shown and user remains on login screen. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{POS Product Listing Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-03: POS Product Listing}
	\label{tab:tc_pos_list}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-03 \\ \hline
		\textbf{Brief Description} & Verify POS product listing loads correctly with price and stock status. \\ \hline
		\textbf{Precondition} & Products exist in database; POS user is logged in. \\ \hline
		\textbf{Steps} & Open POS Dashboard $\rightarrow$ Navigate to Product Listing. \\ \hline
		\textbf{Expected Result} & Product list loads successfully; each item shows price and availability/stock status. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{POS Add Product Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-04: POS Add Product}
	\label{tab:tc_pos_add}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-04 \\ \hline
		\textbf{Brief Description} & Validate adding a new product through POS add product interface. \\ \hline
		\textbf{Precondition} & POS user has permission to add products; required fields are known. \\ \hline
		\textbf{Steps} & Open Add Product $\rightarrow$ Enter product details $\rightarrow$ Submit. \\ \hline
		\textbf{Expected Result} & Product is created successfully and visible in product listing. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{POS Sale Transaction Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-05: POS Sale Transaction}
	\label{tab:tc_pos_sale}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-05 \\ \hline
		\textbf{Brief Description} & Validate that a sale transaction completes and updates inventory correctly. \\ \hline
		\textbf{Precondition} & Product stock is available; POS user is logged in. \\ \hline
		\textbf{Steps} & Select product $\rightarrow$ Add to sale $\rightarrow$ Confirm transaction. \\ \hline
		\textbf{Expected Result} & Sale is recorded successfully and product stock quantity is reduced accordingly. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{Franchise Creation Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-06: Add Franchise}
	\label{tab:tc_franchise_add}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-06 \\ \hline
		\textbf{Brief Description} & Verify that Super Admin can create a new franchise successfully. \\ \hline
		\textbf{Precondition} & Admin account is logged in; required fields are available. \\ \hline
		\textbf{Steps} & Open Franchise Module $\rightarrow$ Add Franchise $\rightarrow$ Enter details $\rightarrow$ Save. \\ \hline
		\textbf{Expected Result} & Franchise is created and appears in franchise dashboard list. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{City Assignment Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-07: City Assignment to Franchise}
	\label{tab:tc_city_assign}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-07 \\ \hline
		\textbf{Brief Description} & Validate that a city can be assigned to a franchise for controlled regional operations. \\ \hline
		\textbf{Precondition} & Franchise exists; Admin has permissions. \\ \hline
		\textbf{Steps} & Open City Management $\rightarrow$ Select franchise $\rightarrow$ Add/Assign city $\rightarrow$ Save. \\ \hline
		\textbf{Expected Result} & City is linked to the franchise and appears in assigned region list. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{Contract Creation Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-08: Add Contract}
	\label{tab:tc_contract_add}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-08 \\ \hline
		\textbf{Brief Description} & Validate creation of a new contract between platform and franchise/store. \\ \hline
		\textbf{Precondition} & Admin account logged in; related franchise/store exists. \\ \hline
		\textbf{Steps} & Open Contract Module $\rightarrow$ Add Contract $\rightarrow$ Enter terms/details $\rightarrow$ Save. \\ \hline
		\textbf{Expected Result} & Contract is created and visible in contract listing dashboard. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{Contract Proposal Approval/Rejection Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-09: Approve/Reject Contract Proposal}
	\label{tab:tc_contract_approve}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-09 \\ \hline
		\textbf{Brief Description} & Verify admin can approve or reject a submitted contract proposal and status is updated. \\ \hline
		\textbf{Precondition} & Proposal exists in proposals list; Admin is logged in. \\ \hline
		\textbf{Steps} & Open Proposals $\rightarrow$ Select proposal $\rightarrow$ Click Approve/Reject. \\ \hline
		\textbf{Expected Result} & Proposal status changes accordingly and reflects in proposal/contract listing. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\subsection{Order Status Update and Tracking Test Case}
\begin{table}[H]
	\centering
	\caption{Test Case TC-10: Order Status Update and Tracking}
	\label{tab:tc_order_tracking}
	\begin{tabular}{p{0.27\textwidth} p{0.65\textwidth}}
		\hline
		\textbf{Test Case ID} & TC-10 \\ \hline
		\textbf{Brief Description} & Validate order lifecycle updates and visibility in order management dashboards. \\ \hline
		\textbf{Precondition} & Order exists in system; authorized role (Store Manager/Franchise Admin) is logged in. \\ \hline
		\textbf{Steps} & Open Orders $\rightarrow$ Select order $\rightarrow$ Update status (e.g., Pending $\rightarrow$ Processing $\rightarrow$ Completed). \\ \hline
		\textbf{Expected Result} & Status updates are saved and reflected in the order listing and order details view. \\ \hline
		\textbf{Status} & Pass \\ \hline
	\end{tabular}
\end{table}

\section{Summary}
This chapter presented the software testing process carried out for the Barqi Bazar platform.
Testing techniques including unit testing, integration testing, functional testing, performance testing,
security testing, and user acceptance testing were applied to validate the correctness and stability of
all major workflows.

The executed test cases confirmed that authentication, POS operations, franchise governance,
contract management, and order lifecycle handling function as expected. The results demonstrate that
the system maintains data accuracy, enforces role based security, and remains stable under normal
operational use. Overall, the testing phase confirms that Barqi Bazar is ready for deployment.
