
\section{Appendices}
In this section, we provide supplementary material to enhance and support the content presented in the previous chapters. The appendices include a range of additional details, diagrams, and documentation that are directly related to the “Cloud-based Market-oriented Point of Sale System.” These supplementary resources are designed to offer further clarification on key aspects of the system, elaborating on its design, development, and functionality. The appendices contain technical specifications, system architecture diagrams, flowcharts, and documentation that explain various elements of the system in greater detail. These materials help provide a clearer understanding of how the system was designed to meet the specific needs of small and medium-sized businesses. Additionally, they may include user manuals, installation guides, and code snippets that give readers an in-depth look at the structure and operation of the system. By offering these additional resources, we aim to provide a comprehensive reference for anyone looking to understand the system more thoroughly. Whether for developers, business owners, or other stakeholders, the appendices serve as an invaluable source of information, helping users to appreciate the technical intricacies, operational features, and the overall purpose of the POS system. These materials ensure that all aspects of the system’s development and functionality are transparent, helping to further solidify its relevance and effectiveness in real-world business.

Furthermore, the appendices may include detailed test results, case studies, and examples of how the system performs under different conditions, helping to showcase its reliability and efficiency in practical scenarios. Diagrams illustrating the flow of data between the desktop and web applications, as well as the cloud database, provide a visual understanding of the system’s architecture and data management processes. These resources offer valuable insights into the decision-making process behind the design choices, ensuring that readers can fully grasp the reasoning behind the system’s structure. Overall, the appendices serve as a comprehensive and detailed guide, offering transparency and further context to the content covered throughout the chapters.

\section{Appendix A: Glossary}
\begin{table}[H]
\centering
\caption{Glossary of Terms}
\begin{tabular}{|p{0.2\linewidth}|p{0.7\linewidth}|}
\hline
\textbf{Term} & \textbf{Definition} \\ \hline
POS & Point of Sale \\ \hline
UI & User Interface \\ \hline
API & Application Programming Interface \\ \hline
PDF & Portable Document Format \\ \hline
CSV & Comma-Separated Values \\ \hline
UAT & User Acceptance Testing \\ \hline
CRUD & Create, Read, Update, and Delete \\ \hline
HTTPS & Hypertext Transfer Protocol Secure \\ \hline
MFA & Multi-Factor Authentication \\ \hline
SQL & Structured Query Language \\ \hline
MDI & Multiple Document Interface \\ \hline
IDE & Integrated Development Environment \\ \hline
PouchDB & Portable Database \\ \hline
CouchDB & Cluster Of Unreliable Commodity Hardware Database \\ \hline
HTML & Hypertext Markup Language \\ \hline
CSS & Cascading Style Sheets \\ \hline
UI/UX & User Interface / User Experience \\ \hline
VS Code & Visual Studio Code \\ \hline
db & Database \\ \hline
\end{tabular}
\label{tab:glossary}
\end{table}
